Generating Images From Captions\\ With Attention

### 2015-11-01 iclr-paper-new.tex
u
a

The output of the $\decoder$ function $\hdec_t$ is then passed through the $\writeop$ operator 
which is added to a cumulative canvas matrix $c_t \in \real^{h \times w}$, with $c_0=0$ (\Eqref{eq:writeop}). 
%\FIXME{Jimmy, could you put more about the write operator}. 
%The $\writeop$ operator
%applies an array of Gaussian filters on the patch, placing 
%it on the canvas $c_t$ with smoothly varying location and zoom (same as 
%defined in \citep{gregor_draw}). 
The $\writeop$ operator produces two arrays of 1D Gaussian filter banks $\gFilterx(\hdec_t)\in\real^{h\times p}$ and $\gFiltery(\hdec_t)\in\real^{w\times p}$ with locations and scales predicted from the generative LSTM hidden state $\hdec_t$ (same as defined in \cite{gregor_draw}). The Gaussian filter banks apply to the generated $p$-by-$p$ image patch $\WriteFunc(\hdec_t) \in \real^{p\times p}$, placing it onto the canvas $c_t$:
\beqa
\label{eq:write}
\Delta \canv_{t-1} = \canv_{t} - \canv_{t-1} = \writeop(\hdec_t) = \gFilterx(\hdec_t) \WriteFunc(\hdec_t) \gFiltery(\hdec_t)^\top. 
\eeqa

Finally, each pixel $\canv_{T,i}$ from the final canvas $\canv_T$ is transformed using a sigmoid function $\sigmoid$ to produce a conditional Bernoulli 
distribution with the mean vector $\sigmoid(\canv_{T})$ over the image pixels 
$\oimage$ given the latent variables $\Lat_{1:T}$ and the input caption $\icaption$.

@@

\subsection*{Acknowledgements}
This work was supported by Samsung and IARPA, Raytheon BBN Contract No. D11PC20071.
We would like to thank developers of Theano \citep{theano}, the authors of \citep{denton_lapgan} for open sourcing their code, and Ryan Kiros and Nitish Srivastava for helpful discussions. 
%We will be releasing our code with pretrained models.

>>>>

The output of the $\decoder$ function $\hdec_t$ is then passed through the $\writeop$ operator 
which is added to a cumulative canvas matrix $c_t \in \real^{h \times w}$, with $c_0=0$ (\Eqref{eq:writeop}). 
%\FIXME{Jimmy, could you put more about the write operator}. 
%The $\writeop$ operator
%applies an array of Gaussian filters on the patch, placing 
%it on the canvas $c_t$ with smoothly varying location and zoom (same as 
%defined in \citep{gregor_draw}). 
The $\writeop$ operator produces two arrays of 1D Gaussian filter banks $\gFilterx(\hdec_t)\in\real^{h\times p}$ and $\gFiltery(\hdec_t)\in\real^{w\times p}$ with locations and scales predicted from the generative LSTM hidden state $\hdec_t$ (same as defined in \cite{gregor_draw}). The Gaussian filter banks apply to the generated $p$-by-$p$ image patch $\WriteFunc(\hdec_t) \in \real^{p\times p}$, placing it onto the canvas $c_t$:
\beqa
\label{eq:write}
\Delta \canv_{t} = \canv_{t} - \canv_{t-1} = \writeop(\hdec_t) = \gFilterx(\hdec_t) \WriteFunc(\hdec_t) \gFiltery(\hdec_t)^\top. 
\eeqa

Finally, each entry $\canv_{T,i}$ from the final canvas matrix $\canv_T$ is transformed using a sigmoid function $\sigmoid$ to produce a conditional Bernoulli 
distribution with the mean vector $\sigmoid(\canv_{T})$ over the 
$h\times w$ image pixels~$\oimage$ given the latent variables 
$\Lat_{1:T}$ and the input caption $\icaption$.\footnote{We also experimented with a conditional Gaussian observation model, but
it worked much worse compared to the Benoulli model.}

@@

{\small
{\bf Acknowledgements:}
This work was supported by Samsung and IARPA, Raytheon BBN Contract No. D11PC20071.
We would like to thank developers of Theano \citep{theano}, the authors of \citep{denton_lapgan} for open sourcing their code, and Ryan Kiros and Nitish Srivastava for helpful discussions. 
%We will be releasing our code with pretrained models.
}
